---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

[![Travis-CI Build Status](https://travis-ci.org/diffform/IMOMBOX.svg?branch=master)](https://travis-ci.org/diffform/IMOMBOX)


# IMOMBOX

This is an `R` implementation of the original Matlab code of Matthias Held ("matthias.held@whu.edu") to calculate Bakshi/Kapadia/Madan moments of option implied return distribution.

**CURRENTLY THIS PACKAGE IS UNDER HEAVY DEVELOPMENT AND NOT ALL THE FUNCTIONS HAVE YET BEEN IMPLEMENTED TO THEIR FULL EXTENT!**

## Installation

You can install IMOMBOX from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("diffform/IMOMBOX")
```

## Example

The example data is provided in the  originally matlab package and contains observations of call and put option prices from `2013-09-20` written on the German DAX index with a maturity of `2013-10-18` (28 days to maturity). Based on these options we calculate risk neutral prices for the first four moment contracts, i.e. the contracts that pay $R^1$, $R^2$, $R^3$ and $R^4$.

```{r example1}
require(IMOMBOX)
data(DAX)
# Only use Strikes and prices, have R calculate S0 and df
Option2price(DAX$XC,DAX$C,DAX$XP,DAX$P)
```

So, we find that an option that pays $R^2$ in 28 days from now commands a price of `r round(Option2price(DAX$XC,DAX$C,DAX$XP,DAX$P)[2],4)`.

